Fractional Types

### 2016-12-19 typespp.tex
removed sec 5 because too complex to deal with synch in the time we have

The remainder of the paper is organized as follows. We start by reviewing
necessary background material, consisting of the language $\Pi$ for programming
with isomorphisms or equivalences in a reversible information-preserving way.
Sec.~4 explains the main novel semantic ideas of using $\Pi$ programs to
generate non-trivial groupoids with fractional cardinality, as well as
translating the semantic ideas into an extension of $\Pi$ with new type
constructors denoting non-trivial groupoids and new programs that manipulate
such types.  Sec.~5 presents some example programs to illustrate the
expressiveness of the language.  The last section puts our work in perspective
and concludes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{$\Pi^/$: Additional Examples}

Compact closed categories support various interesting constructions, such as
duals, name and coname, and trace, which eventually lead to a certain notion of
recursive higher-order functions~\cite{abramsky-2008}.  We illustrate the
expressiveness of $\Pi^/$ by defining these constructions.

%%%%%%%%%%
\subsection{\texttt{dual}}

Given a \textrm{/-combinator} $p : \#c \leftrightblackspoon \#d$,
we can define a \emph{dual morphism}
$p^{\ast} : 1/\#d \leftrightblackspoon 1/\#c$. This is shown by building a
reversible circuit in Fig.~\ref{fig:dual}.  The highlights that seem to
``escape'' the circuit indicate that \emph{dual} can only be used in a
context with at least one quantifier being present.

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path [highlight] (-1,1) edge node[above] {} (0,1);
    \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (0,1);

    \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
    \node at (0.5,1) {\footnotesize{$\unitetl/$}};

    \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);

    \draw (2,0.75) -- (3,0.75) -- (3,2.75) -- (2,2.75) -- cycle;
    \node at (2.5,1.75) {\footnotesize{$\eta +$}};

    \draw[dashed] (3.2,1.25) -- (3.2,2.25);
    \path [highlight] (3,2.25) edge node[above] {} (8,2.25);
    \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (8,2.25);
    \path [highlight] (3,1.25) edge node[above] {} (4,1.25);
    \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#c}$}} (4,1.25);

    \draw (4,0.75) -- (5,0.75) -- (5,1.75) -- (4,1.75) -- cycle;
    \node at (4.5,1.25) {\footnotesize{$p$}};

    \draw[dashed] (5.8,0.25) -- (5.8,1.25);
    \path [highlight] (1,0.25) edge node[above] {} (6,0.25);
    \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (6,0.25);
    \path [highlight] (5,1.25) edge node[above] {} (6,1.25);
    \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

    \draw (6,-0.25) -- (7,-0.25) -- (7,1.75) -- (6,1.75) -- cycle;
    \node at (6.5,0.75) {\footnotesize{$\epsilon +$}};

    \path (7,0.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (8,0.75);

    \draw (8,0.5) -- (9,0.5) -- (9,2.5) -- (8,2.5) -- cycle;
    \node at (8.5,1.5) {\footnotesize{$\unititl/$}};

    \path [highlight] (9,1.5) edge node[above] {} (10,1.5);
    \path (9,1.5) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (10,1.5);
  \end{tikzpicture}
  \caption{\label{fig:dual} Dual}
\end{figure}

%%%
\subsection{\texttt{name} and \texttt{coname}}

Each morphism $\rho_\bullet : \order{c} \leftrightblackspoon \order{d}$ can be
given a \emph{name} and a \emph{coname}. As shown in Fig.~\ref{fig:name-coname}.
the name of $\rho_\bullet$ denoted $\ulcorner{\rho_\bullet}\urcorner$ has type
$\order{\idiso} \leftrightblackspoon \iorder{c} \circledast \order{d}$ and the
coname of $\rho_\bullet$ denoted $\llcorner{\rho_\bullet}\lrcorner$ has type
$\iorder{c} \circledast \order{d} \leftrightblackspoon \order{\idiso}$.
Intuitively, this means that for each morphism of type
$\order{c} \leftrightblackspoon \order{d}$, it is possible to construct from
``nothing'' an object $\iorder{c} \circledast \order{d}$ in the category that
denotes this morphism and dually to eliminate this object. Like with the case
for the dual construction, we need to insert a combinator \emph{under} a
quantifier.

\begin{figure}[htb]
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
      \path (-1.1,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,1);

      \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
      \node at (0.5,1) {\footnotesize{$\eta -$}};

      \path [highlight] (1,1.75) edge node[above] {} (4,1.75);
      \path (1,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (4,1.75);

      \path [highlight] (1,0.25) edge node[above] {} (2,0.25);
      \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,0.25);
      \draw[dashed] (1.25,1.75) -- (1.25,0.25);

      \draw (2,0) -- (3,0) -- (3,0.5) -- (2,0.5) -- cycle;
      \node at (2.5,0.25) {\footnotesize{$\rho_\bullet$}};

      \path [highlight] (3,0.25) edge node[above] {} (4,0.25);
      \path (3,0.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,0.25);

    \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]

      \path [highlight] (-1.1,1.75) edge node[above] {} (2,1.75);
      \path (-1.1,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (2,1.75);

      \path [highlight] (-1.1,0.25) edge node[above] {} (0,0.25);
      \path (-1.1,0.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (0,0.25);

      \draw (0,0) -- (1,0) -- (1,0.5) -- (0,0.5) -- cycle;
      \node at (0.50,0.25) {\footnotesize{$\rho_\bullet^{-1}$}};

      \path [highlight] (1,0.25) edge node[above] {} (2,0.25);
      \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,0.25);
      \draw[dashed] (1.75,1.75) -- (1.75,0.25);

      \draw (2,0) -- (3,0) -- (3,2) -- (2,2) -- cycle;
      \node at (2.5,1) {\footnotesize{$\epsilon +$}};

      \path (3,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (4,1);
    \end{tikzpicture}
  \end{subfigure}
  \caption{\label{fig:name-coname} \texttt{name} and \texttt{coname},
  where $p : \#c \leftrightblackspoon \#d$}
\end{figure}

%%%
\subsection{Higher-Order Functions}

As shown above, names and conames encode a morphism of type
$\order{c} \leftrightblackspoon \order{d}$ using morphisms between $\order{id}$
and $\iorder{c} \circledast \order{d}$. These names and conames give rise to a
notion of higher-order function that can be composed and applied. Given two
morphisms of types $\order{c} \leftrightblackspoon \order{d}$ and
$\order{d} \leftrightblackspoon \order{d}$, we can compose their names to get
the name of their sequential composition. Given the name of a morphism
$\order{c} \leftrightblackspoon \order{d}$ and given a value of type
$\order{c}$, we can produce a value of type $\order{d}$ effectively ``applying''
the morphism.

%%%
\subsection{Trace}

Traced categories~\cite{joyal1996traced} have proved useful for modeling
recursion~\cite{Hasegawa:1997:RCS:645893.671607}. It is interesting that every
compact closed category admits a trace which we can implement as shown below. In
the figure, we show that given a combinator
$\rho_\bullet : \order{c} \circledast \order{d} \leftrightblackspoon \order{c}
\circledast \order{e}$
we can construct a circuit of type $\order{d} \leftrightblackspoon \order{e}$
that typechecks iff we have a fixed point for $f$ for the argument of type
$\order{c}$.

FIX TRACE

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path [highlight] (-1,1) edge node[above] {} (0,1);
    \path (-1,1) edge node[above] {\footnotesize{$\order{d}$}} (0,1);

    \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
    \node at (0.5,1) {\footnotesize{$\unitetl/$}};

    \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);

    \draw (2,0.75) -- (3,0.75) -- (3,2.75) -- (2,2.75) -- cycle;
    \node at (2.5,1.75) {\footnotesize{$\eta +$}};

    \draw[dashed] (3.2,1.25) -- (3.2,2.25);
    \path [highlight] (3,2.25) edge node[above] {} (8,2.25);
    \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (8,2.25);
    \path [highlight] (3,1.25) edge node[above] {} (4,1.25);
    \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#c}$}} (4,1.25);

    \draw (4,0.75) -- (5,0.75) -- (5,1.75) -- (4,1.75) -- cycle;
    \node at (4.5,1.25) {\footnotesize{$p$}};

    \draw[dashed] (5.8,0.25) -- (5.8,1.25);
    \path [highlight] (1,0.25) edge node[above] {} (6,0.25);
    \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (6,0.25);
    \path [highlight] (5,1.25) edge node[above] {} (6,1.25);
    \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

    \draw (6,-0.25) -- (7,-0.25) -- (7,1.75) -- (6,1.75) -- cycle;
    \node at (6.5,0.75) {\footnotesize{$\epsilon +$}};

    \path (7,0.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (8,0.75);

    \draw (8,0.5) -- (9,0.5) -- (9,2.5) -- (8,2.5) -- cycle;
    \node at (8.5,1.5) {\footnotesize{$\unititl/$}};

    \path [highlight] (9,1.5) edge node[above] {} (10,1.5);
    \path (9,1.5) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (10,1.5);
  \end{tikzpicture}
  \caption{\label{fig:trace} Trace}
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path (-1,2) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,2);
    \path (-1,0.5) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,0.5);

    \draw (0,-0.25) -- (1,-0.25) -- (1,1.5) -- (0,1.5) -- cycle;
    \node at (0.5,0.6) {\footnotesize{$\textsf{name}_p$}};

    \path (1,1.25) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (2,1.25);
    \path (1,0) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,0);

    \draw (2,1) -- (3,1) -- (3,2.25) -- (2,2.25) -- cycle;
    \node at (2.5,1.625) {\footnotesize{$\epsilon +$}};

    \path (3,1.625) edge node[above] {\footnotesize{$\textsf{\#id}$}} (4,1.625);

    \draw (4,-0.25) -- (5,-0.25) -- (5,2) -- (4,2) -- cycle;
    \node at (4.5,0.85) {\footnotesize{$\unititl/$}};

    \path (5,0.85) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,0.85);
  \end{tikzpicture}
  \caption{\label{fig:apply} apply}
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path (-1,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,1);

    \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
    \node at (0.5,1) {\footnotesize{$\unitetl/$}};

    \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);
    \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,0.25);

    \draw (2,1.25) -- (3,1.25) -- (3,2.25) -- (2,2.25) -- cycle;
    \node at (2.5,1.75) {\footnotesize{$\textsf{name}_{p_1}$}};

    \path (3,2.125) edge node[above] {\footnotesize{${1/\textsf{\#c}}$}} (8,2.125);
    \path (3,1.375) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,1.375);

    \draw (2,0.75) -- (3,0.75) -- (3,-0.25) -- (2,-0.25) -- cycle;
    \node at (2.5,0.25) {\footnotesize{$\textsf{name}_{p_2}$}};

    \path (3,0.625) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (4,0.625);
    \path (3,-0.125) edge node[above] {\footnotesize{${\textsf{\#e}}$}} (6,-0.125);

    \draw (4,1.5) -- (5,1.5) -- (5,0.5) -- (4,0.5) -- cycle;
    \node at (4.5,1) {\footnotesize{$\epsilon +$}};

    \path (5,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (6,1);

    \draw (6,1.125) -- (7,1.125) -- (7,-0.25) -- (6,-0.25) -- cycle;
    \node at (6.5,0.5) {\footnotesize{$\unititl/$}};

    \path (7,0.5) edge node[above] {\footnotesize{${\textsf{\#e}}$}} (8,0.5);
  \end{tikzpicture}
  \caption{\label{fig:compose} compose}
\end{figure}

>>>>

The remainder of the paper is organized as follows. We start by reviewing
necessary background material, consisting of the language $\Pi$ for programming
with isomorphisms or equivalences in a reversible information-preserving way.
Sec.~4 explains the main novel semantic ideas of using $\Pi$ programs to
generate non-trivial groupoids with fractional cardinality, as well as
translating the semantic ideas into an extension of $\Pi$ with new type
constructors denoting non-trivial groupoids and new programs that manipulate
such types. The last section puts our work in perspective and concludes.

@@

%%%%
\subsection{Additional Examples}

Compact closed categories support various interesting
constructions~\cite{abramsky-2008}, such as duals, name and coname, and
trace~\cite{joyal1996traced,Hasegawa:1997:RCS:645893.671607}, which eventually
lead to a certain notion of recursive higher-order functions. These
constructions do not immediately transfer to the context of $\Pi^/$ as we have
explicit quantifiers and synchronization primitives that are not present in the
conventional setting. Resolving these subtleties will provide the first
operational interpretation known to us of multiplicative higher-order recursive
functions.

% \begin{figure}[htb]
%   \centering
%   \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
%     \path [highlight] (-1,1) edge node[above] {} (0,1);
%     \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (0,1);

%     \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
%     \node at (0.5,1) {\footnotesize{$\unitetl/$}};

%     \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);

%     \draw (2,0.75) -- (3,0.75) -- (3,2.75) -- (2,2.75) -- cycle;
%     \node at (2.5,1.75) {\footnotesize{$\eta +$}};

%     \draw[dashed] (3.2,1.25) -- (3.2,2.25);
%     \path [highlight] (3,2.25) edge node[above] {} (8,2.25);
%     \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (8,2.25);
%     \path [highlight] (3,1.25) edge node[above] {} (4,1.25);
%     \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#c}$}} (4,1.25);

%     \draw (4,0.75) -- (5,0.75) -- (5,1.75) -- (4,1.75) -- cycle;
%     \node at (4.5,1.25) {\footnotesize{$p$}};

%     \draw[dashed] (5.8,0.25) -- (5.8,1.25);
%     \path [highlight] (1,0.25) edge node[above] {} (6,0.25);
%     \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (6,0.25);
%     \path [highlight] (5,1.25) edge node[above] {} (6,1.25);
%     \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

%     \draw (6,-0.25) -- (7,-0.25) -- (7,1.75) -- (6,1.75) -- cycle;
%     \node at (6.5,0.75) {\footnotesize{$\epsilon +$}};

%     \path (7,0.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (8,0.75);

%     \draw (8,0.5) -- (9,0.5) -- (9,2.5) -- (8,2.5) -- cycle;
%     \node at (8.5,1.5) {\footnotesize{$\unititl/$}};

%     \path [highlight] (9,1.5) edge node[above] {} (10,1.5);
%     \path (9,1.5) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (10,1.5);
%   \end{tikzpicture}
%   \caption{\label{fig:dual} Dual}
% \end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{$\Pi^/$: Additional Examples}

% Compact closed categories support various interesting constructions, such as
% duals, name and coname, and trace, which eventually lead to a certain notion of
% recursive higher-order functions~\cite{abramsky-2008}.  We illustrate the
% expressiveness of $\Pi^/$ by defining duals, name and coname, and a higher-order
% \emph{apply} combinator.

% %%%%%%%%%%
% \subsection{\texttt{dual}}

% Given a \textrm{/-combinator} $p : \#c \leftrightblackspoon \#d$,
% we can define a \emph{dual morphism}
% $p^{\ast} : 1/\#d \leftrightblackspoon 1/\#c$. This is shown by building a
% reversible circuit in Fig.~\ref{fig:dual}.  The highlights that seem to
% ``escape'' the circuit indicate that \emph{dual} can only be used in a
% context with at least one quantifier being present.

% \begin{figure}[htb]
%   \centering
%   \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
%     \path [highlight] (-1,1) edge node[above] {} (0,1);
%     \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (0,1);

%     \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
%     \node at (0.5,1) {\footnotesize{$\unitetl/$}};

%     \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);

%     \draw (2,0.75) -- (3,0.75) -- (3,2.75) -- (2,2.75) -- cycle;
%     \node at (2.5,1.75) {\footnotesize{$\eta +$}};

%     \draw[dashed] (3.2,1.25) -- (3.2,2.25);
%     \path [highlight] (3,2.25) edge node[above] {} (8,2.25);
%     \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (8,2.25);
%     \path [highlight] (3,1.25) edge node[above] {} (4,1.25);
%     \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#c}$}} (4,1.25);

%     \draw (4,0.75) -- (5,0.75) -- (5,1.75) -- (4,1.75) -- cycle;
%     \node at (4.5,1.25) {\footnotesize{$p$}};

%     \draw[dashed] (5.8,0.25) -- (5.8,1.25);
%     \path [highlight] (1,0.25) edge node[above] {} (6,0.25);
%     \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (6,0.25);
%     \path [highlight] (5,1.25) edge node[above] {} (6,1.25);
%     \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

%     \draw (6,-0.25) -- (7,-0.25) -- (7,1.75) -- (6,1.75) -- cycle;
%     \node at (6.5,0.75) {\footnotesize{$\epsilon +$}};

%     \path (7,0.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (8,0.75);

%     \draw (8,0.5) -- (9,0.5) -- (9,2.5) -- (8,2.5) -- cycle;
%     \node at (8.5,1.5) {\footnotesize{$\unititl/$}};

%     \path [highlight] (9,1.5) edge node[above] {} (10,1.5);
%     \path (9,1.5) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (10,1.5);
%   \end{tikzpicture}
%   \caption{\label{fig:dual} Dual}
% \end{figure}

% %%%
% \subsection{\texttt{name} and \texttt{coname}}

% Each morphism $\rho_\bullet : \order{c} \leftrightblackspoon \order{d}$ can be
% given a \emph{name} and a \emph{coname}. As shown in Fig.~\ref{fig:name-coname}.
% the name of $\rho_\bullet$ denoted $\ulcorner{\rho_\bullet}\urcorner$ has type
% $\order{\idiso} \leftrightblackspoon \iorder{c} \circledast \order{d}$ and the
% coname of $\rho_\bullet$ denoted $\llcorner{\rho_\bullet}\lrcorner$ has type
% $\iorder{c} \circledast \order{d} \leftrightblackspoon \order{\idiso}$.
% Intuitively, this means that for each morphism of type
% $\order{c} \leftrightblackspoon \order{d}$, it is possible to construct from
% ``nothing'' an object $\iorder{c} \circledast \order{d}$ in the category that
% denotes this morphism and dually to eliminate this object. Like with the case
% for the dual construction, we need to insert a combinator \emph{under} a
% quantifier.

% \begin{figure}[htb]
%   \begin{subfigure}{.5\textwidth}
%     \centering
%     \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
%       \path (-1.1,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,1);

%       \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
%       \node at (0.5,1) {\footnotesize{$\eta -$}};

%       \path [highlight] (1,1.75) edge node[above] {} (4,1.75);
%       \path (1,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (4,1.75);

%       \path [highlight] (1,0.25) edge node[above] {} (2,0.25);
%       \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,0.25);
%       \draw[dashed] (1.25,1.75) -- (1.25,0.25);

%       \draw (2,0) -- (3,0) -- (3,0.5) -- (2,0.5) -- cycle;
%       \node at (2.5,0.25) {\footnotesize{$\rho_\bullet$}};

%       \path [highlight] (3,0.25) edge node[above] {} (4,0.25);
%       \path (3,0.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,0.25);

%     \end{tikzpicture}
%   \end{subfigure}
%   \begin{subfigure}{.5\textwidth}
%     \centering
%     \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]

%       \path [highlight] (-1.1,1.75) edge node[above] {} (2,1.75);
%       \path (-1.1,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (2,1.75);

%       \path [highlight] (-1.1,0.25) edge node[above] {} (0,0.25);
%       \path (-1.1,0.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (0,0.25);

%       \draw (0,0) -- (1,0) -- (1,0.5) -- (0,0.5) -- cycle;
%       \node at (0.50,0.25) {\footnotesize{$\rho_\bullet^{-1}$}};

%       \path [highlight] (1,0.25) edge node[above] {} (2,0.25);
%       \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,0.25);
%       \draw[dashed] (1.75,1.75) -- (1.75,0.25);

%       \draw (2,0) -- (3,0) -- (3,2) -- (2,2) -- cycle;
%       \node at (2.5,1) {\footnotesize{$\epsilon +$}};

%       \path (3,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (4,1);
%     \end{tikzpicture}
%   \end{subfigure}
%   \caption{\label{fig:name-coname} \texttt{name} and \texttt{coname},
%   where $p : \#c \leftrightblackspoon \#d$}
% \end{figure}

% %%%
% \subsection{Higher-Order Functions}

% As shown above, names and conames encode a morphism of type
% $\order{c} \leftrightblackspoon \order{d}$ using morphisms between $\order{id}$
% and $\iorder{c} \circledast \order{d}$. These names and conames give rise to a
% notion of higher-order function that can be composed and applied. Given two
% morphisms of types $\order{c} \leftrightblackspoon \order{d}$ and
% $\order{d} \leftrightblackspoon \order{d}$, we can compose their names to get
% the name of their sequential composition. Given the name of a morphism
% $\order{c} \leftrightblackspoon \order{d}$ and given a value of type
% $\order{c}$, we can produce a value of type $\order{d}$ effectively ``applying''
% the morphism.

% %%%
% \subsection{Trace}

% Traced categories~\cite{joyal1996traced} have proved useful for modeling
% recursion~\cite{Hasegawa:1997:RCS:645893.671607}. It is interesting that every
% compact closed category admits a trace which we can implement as shown below. In
% the figure, we show that given a combinator
% $\rho_\bullet : \order{c} \circledast \order{d} \leftrightblackspoon \order{c}
% \circledast \order{e}$
% we can construct a circuit of type $\order{d} \leftrightblackspoon \order{e}$
% that typechecks iff we have a fixed point for $f$ for the argument of type
% $\order{c}$.

% FIX TRACE

% \begin{figure}[htb]
%   \centering
%   \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
%     \path [highlight] (-1,1) edge node[above] {} (0,1);
%     \path (-1,1) edge node[above] {\footnotesize{$\order{d}$}} (0,1);

%     \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
%     \node at (0.5,1) {\footnotesize{$\unitetl/$}};

%     \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);

%     \draw (2,0.75) -- (3,0.75) -- (3,2.75) -- (2,2.75) -- cycle;
%     \node at (2.5,1.75) {\footnotesize{$\eta +$}};

%     \draw[dashed] (3.2,1.25) -- (3.2,2.25);
%     \path [highlight] (3,2.25) edge node[above] {} (8,2.25);
%     \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (8,2.25);
%     \path [highlight] (3,1.25) edge node[above] {} (4,1.25);
%     \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#c}$}} (4,1.25);

%     \draw (4,0.75) -- (5,0.75) -- (5,1.75) -- (4,1.75) -- cycle;
%     \node at (4.5,1.25) {\footnotesize{$p$}};

%     \draw[dashed] (5.8,0.25) -- (5.8,1.25);
%     \path [highlight] (1,0.25) edge node[above] {} (6,0.25);
%     \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (6,0.25);
%     \path [highlight] (5,1.25) edge node[above] {} (6,1.25);
%     \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

%     \draw (6,-0.25) -- (7,-0.25) -- (7,1.75) -- (6,1.75) -- cycle;
%     \node at (6.5,0.75) {\footnotesize{$\epsilon +$}};

%     \path (7,0.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (8,0.75);

%     \draw (8,0.5) -- (9,0.5) -- (9,2.5) -- (8,2.5) -- cycle;
%     \node at (8.5,1.5) {\footnotesize{$\unititl/$}};

%     \path [highlight] (9,1.5) edge node[above] {} (10,1.5);
%     \path (9,1.5) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (10,1.5);
%   \end{tikzpicture}
%   \caption{\label{fig:trace} Trace}
% \end{figure}

% \begin{figure}[htb]
%   \centering
%   \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
%     \path (-1,2) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,2);
%     \path (-1,0.5) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,0.5);

%     \draw (0,-0.25) -- (1,-0.25) -- (1,1.5) -- (0,1.5) -- cycle;
%     \node at (0.5,0.6) {\footnotesize{$\textsf{name}_p$}};

%     \path (1,1.25) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (2,1.25);
%     \path (1,0) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,0);

%     \draw (2,1) -- (3,1) -- (3,2.25) -- (2,2.25) -- cycle;
%     \node at (2.5,1.625) {\footnotesize{$\epsilon +$}};

%     \path (3,1.625) edge node[above] {\footnotesize{$\textsf{\#id}$}} (4,1.625);

%     \draw (4,-0.25) -- (5,-0.25) -- (5,2) -- (4,2) -- cycle;
%     \node at (4.5,0.85) {\footnotesize{$\unititl/$}};

%     \path (5,0.85) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,0.85);
%   \end{tikzpicture}
%   \caption{\label{fig:apply} apply}
% \end{figure}

% \begin{figure}[htb]
%   \centering
%   \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
%     \path (-1,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,1);

%     \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
%     \node at (0.5,1) {\footnotesize{$\unitetl/$}};

%     \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);
%     \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,0.25);

%     \draw (2,1.25) -- (3,1.25) -- (3,2.25) -- (2,2.25) -- cycle;
%     \node at (2.5,1.75) {\footnotesize{$\textsf{name}_{p_1}$}};

%     \path (3,2.125) edge node[above] {\footnotesize{${1/\textsf{\#c}}$}} (8,2.125);
%     \path (3,1.375) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,1.375);

%     \draw (2,0.75) -- (3,0.75) -- (3,-0.25) -- (2,-0.25) -- cycle;
%     \node at (2.5,0.25) {\footnotesize{$\textsf{name}_{p_2}$}};

%     \path (3,0.625) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (4,0.625);
%     \path (3,-0.125) edge node[above] {\footnotesize{${\textsf{\#e}}$}} (6,-0.125);

%     \draw (4,1.5) -- (5,1.5) -- (5,0.5) -- (4,0.5) -- cycle;
%     \node at (4.5,1) {\footnotesize{$\epsilon +$}};

%     \path (5,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (6,1);

%     \draw (6,1.125) -- (7,1.125) -- (7,-0.25) -- (6,-0.25) -- cycle;
%     \node at (6.5,0.5) {\footnotesize{$\unititl/$}};

%     \path (7,0.5) edge node[above] {\footnotesize{${\textsf{\#e}}$}} (8,0.5);
%   \end{tikzpicture}
%   \caption{\label{fig:compose} compose}
% \end{figure}
